Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-03-06 manuscripts/paper-1/main.tex
Intro-State-Method  Verified

    The envision of a digital twin emerged from Grieves'es conceptual model, which was called mirrored spaces model in 2002~\cite{Originsofdigitaltwinconcept},
    and later referenced in a 2005 journal article~\cite{2005JournayArticle}. 
    Furthermore, he introduced the information mirroring model, which was his ideal product lifecycle management tool with only one goal. 
    The goal was to gather as much information about the real system to minimize the waste of the system's sources such as energy, 
    time and material. Initially, this model had four main parts. The real system, 
    virtual system, connection between the real and virtual system and virtual simulations\cite{GrievesPLMBook}. 
    Later, Grieves removed the latter, to simplify the model\cite{Originsofdigitaltwinconcept}. Lastly, after co-authoring with Vicker in 2010, 
    Grieves decided to use the NASA-invented "Digital Twin" word, instead of the information mirroring model\cite{Originsofdigitaltwinconcept}.

    These days, there is evidence that digital twins play a crucial role in the manufacturing industries, 
    life sciences, healthcare, infrastructure and cities\cite{Review2}.
    For example, a digital wind farm from General Electric is a good illustration of how building a digital twin helped to design a better turbine, 
    and later is used to collect and analyze the data from the real system for making the process of the real system more efficient \cite{GeneralElectricWindTurbine}. 
    Another fascinating example of the use of digital twins is Philips' virtual heart model. Twin of the heart evolves with the  data generated by ultrasonic sensors to calculate 
    how well the real heart is pumping the blood This information can be used to predict a potential heart failure, allowing for early intervention and potentially life-saving treatment \cite{PhilipsHearth}. 
    Lastly, FELICE is another interesting example of a digital twin application in manufacturing. In the project, twin models of machines/equipment and 
    agents are utilized to support real-time decision-making, to conduct what-if analyses and experiments. To ensure the quality of these digital twins, a specific Verification \& Validation process is implemented ~\cite{FELICE}.

@@

    \section{State of the art on quality}
    Oxford English Dictionary describes the word quality either as a noun or an adjective. 
    The adjective form indicates, a high standard or excellence. For example, the phrase quality products imply 
    that quality adds a high standard state to the product. Several definitions describe quality 
    as a noun, however, the impactful definition is the quality as a standard of an entity which is measured against the 
    different or the similar entities\cite{OxfordDictionary}. This definition clearly shows the relativity of quality. In addition, quality is defined 
    as the degree to which a set of inherent properties of an entity fulfills the given requirements~\cite{ISO9000}.    
    \subsection{Product quality and Management}
    A product is a tangible or intangible system that satisfies the needs or wants of a customer. It could be a physical system like a car, or an abstract system, like a digital twin. 
    Regarding product quality, there are two different aspects~\cite{GrievesPLMBook}.
    First, quality is an attribute of a product, which meets product specifications. Specifications are mostly defined by the supra-systems subsystems, 
    such as by the stakeholders within the supra-system,  If the stakeholders' expectations, or needs, are met, we can consider high quality.
    The ability to execute to a specific usage standard is the second facet of product quality. Since this standardization is usually not controllable, 
    unlike the first, the system's quality will be determined by how the implied or obligatory standards are fulfilled.

    Quality management systems(QMS) function to plan and execute the organization's quality policies and goals. 
    Examples of such systems can be a standard like ISO 9001 which can provide a framework for an organization, or a data-driven methodology such as Six Sigma to reduce defects and improve efficiency. 
    These concepts are not new, for example, ISO 9001 standard has been established in 1987, and is still being regularly updated ~\cite{ISO90012015}. 
    \subsection{Software quality}
    Software is a combination of programs and data which can be used by virtual 
    systems as well as a physical system like a computer system. In contrast, hardware 
    is a physical subsystem of a computer system\cite{OxfordDictionary}.

    Software Quality is determined by how well software fulfills the requirements that were set. However, those requirements  
    not always reflect what the stakeholders need, hence the quality depends on how accurately these requirements were set \cite{IEE730-2014}. 
    As a result, functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability 
    and portability is the standardized eight attributes that measure software quality \cite{ISO/IEC:25010}.

    Software quality management techniques come from already used manufacturing techniques in the industries. For example, product quality assurance has been used as a 
    software quality management activity with some modifications. For example, in manufacturing, products will never exactly meet a specification, due to errors in the machining which results in some tolerance area. 
    But in the software systems, or more precisely in the virtual systems, it's most of the time, not the case. Also, it's nearly impossible to conclude that, 
    the software product fully meets its specifications. 
    Hence, most of the quality assessments are subjective processes and as a result, the quality attributes should be inspected subjectively \cite{SoftwareEngineering}.

    \subsection{Simulation Quality}
    Simulation models are not merely virtual systems; they are also abstracted systems, 
    which are nothing more than imitations or, to be more precise, abstractions of real systems. 
    Every day, simulation of the real systems occurs in the human brain when the prediction of the future outcome or about the 
    past state of some occurred event required\cite{MobusSystemTheory}. However, most of the simulation processes are computer-based with software programs. Consequently, the idea of simulation software programs emerges. 
    For example, ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} are examples of these simulation software programs.

    Validation and verification are used to evaluate the quality characteristics of the simulation 
    model \cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. 
    Validation is the process of evaluating the simulation quality of the model in comparison to 
    the real system from the perspective of the model's intended applications.
    On the other hand, verification is a procedure to 
    evaluate a simulation model's implementation and its associated 
    data concerning the conceptual description and specifications of the 
    model developer\cite{StewartSimulation,VerificationValidationSergent}.

    Various validation and verification techniques can be employed, which can be broadly categorized into six areas: informal, static, dynamic, symbolic, constraint, 
    and formal techniques \cite{balcicategories}\cite{balcitechniques}. Formal techniques involve mathematical formality, whereas informal techniques rely on human intervention 
    and reasoning. Although mathematical techniques are more precise, informal techniques 
    are more commonly used \cite{balcicategories}. Also, the use of informal techniques does not imply a lack of structure, but rather a reliance on human expertise and interpretation \cite{balcitechniques}.
    \subsection{Digital twin quality}
    To analyze the state of the digital twin quality, a literature analysis was executed. 
    The analysis especially focused on how the digital twin quality is mentioned and assessed within the academic dissertations.

    \subsubsection*{Literature Search Methodology}
    To conduct a thorough literature review on digital twin publications, tools such as Google Scholar and Scopus are utilized. Due to the vast amount of available literature, it is necessary to narrow down the scope of the research. 
    Therefore, a multi-level filtering algorithm is employed to refine the search results.

    The first level of filtering for the literature review on digital twin publications involves specific criteria. These include that dissertation must be written in English and 
    published in a journal or conference and that the search term must be an exact match. To execute this initial filtration, 
    the following queries are used for Google Scholar and Scopus respectively: "search term" and ALL ("digital twin quality") AND (LIMIT-TO (LANGUAGE, "English")).

    After the initial filtering, a second level of manual investigation is necessary. The following criteria are used for this level of filtering:    
    \begin{itemize}
        \item  Eliminating duplicates
        \item  Removing dissertations that are not in English
        \item  Ensuring that selected dissertations have a proper literature review
        \item  Ensuring that abstract and conclusion are relevant to the search term
    \end{itemize}
    If an interesting dissertation(s) would be found during the reading, it will be checked again with the initial filter.
    \subsubsection*{Literature Search Result}
    The search for "digital twin quality" initially resulted in 41 hits on Google Scholar and 3 on Scopus. 
    After the second level of filtering, 6 duplicate dissertations were removed and 10 dissertations that were not in English were also eliminated. 
    This left only 9 dissertations that met all the criteria and were reviewed.

    The search for "digital twin verification" initially resulted in 19 hits on Google Scholar and none on Scopus. 
    After the second level of filtering, one duplicate dissertation was removed and two dissertations that were not in 
    English was also eliminated. As a result, all dissertations were rejected.

    The search for "digital twin validation" initially resulted in 59 hits on Google Scholar and none on Scopus. 
    After the second level of filtering, 4 duplicate dissertations were removed and 4 
    dissertations that were not in English were also eliminated. This left only 8 dissertations that met all the criteria and were reviewed.

    After a thorough review of 17 research papers, several significant findings were revealed.

    First, it was noted that Shcherba et al. focuses on the importance of model quality as an observation for a digital twin subsystem. 
    However, they acknowledged that the quality assessment of the digital twin cannot solely rely on models~\cite{Shcherba}.

    He Zhang et al. developed a consistency evaluation approach for digital twin models, which can be used to assess their quality. 
    The authors also discuss essential concepts, such as consistency between real and virtual systems and ultra-fidelity models. 
    This article emphasizes the improvement of the service component of the digital twin~\cite{ZHANGEVALUATIONMETHOD}.

@@

    Selch et al. present a machine-learning approach based on Bayesian networks to track the quality of the digital twin. 
    The unique aspect of this study is that the authors determine the contributions of subsystems to forecast the overall quality of the digital twin, 
    rather than just analyzing it as a single system. The digital couplings, which are linkages between the subsystems, are also identified as a source of extra uncertainty. 
    However, since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated~\cite{QualityMonitoringofCoupledDigitalTwins}.

@@

    Finally, Shotaro Hamato et al. demonstrated successful real-time anomaly detection using the Unscented Kalman Filter with the digital twin model. 
    However, determining the appropriate threshold for anomaly detection remains an issue~\cite{JapeneseKalmanFilterCorrectness}.

    Overall, these studies provide valuable insights into various aspects of digital twin quality assessment, 
    including model consistency, stability, and validation, as well as machine learning-based approaches and real-time anomaly detection. 
    However, the identified open problems, including modeling realism, data uncertainty, system dynamics, use-case alignment, and reporting invalid modes, 
    call for further research in the field to improve the quality and reliability of digital twins. Moreover, 
    the lack of well-defined quality parameters for digital twins poses a significant challenge in ensuring their quality,
    which necessitates the development of appropriate quality metrics and standards for digital twins.

@@

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%RESULTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Results}
    \begin{table}[h!]
    \begin{center}
    \label{tab:Table1}
    \caption{Mapping of digital twin attributes to the results of the manual reviews: In cases where an attribute is mapped, the "artifact.qualityattribute.value" is incremented by 1. }
    \renewcommand{\arraystretch}{1.25}
    \scalebox{0.70}{
    \begin{tabular}{l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l}
        \textbf{Findings} & \textbf{Correctness} & \textbf{Completeness} & \textbf{Fidelity} & \textbf{Efficiency} & \textbf{Evolvability}\\
        \hline
        \textbf{Finding 1}  &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 2} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 3} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 4} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 5} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 6} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 7} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 8} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 9} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 10} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 11} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 12} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 13} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 14}&~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 15} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 16} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 17} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 18} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 19} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 20} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 21} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
    \end{tabular}
    }
    \end{center}
    \end{table}

>>>>

    The envision of a digital twin emerged from Grieves'es conceptual model, which was called mirrored spaces model in 2002~\cite{Originsofdigitaltwinconcept},
    and later referenced in a 2005 journal article~\cite{2005JournayArticle}. 
    Furthermore, he introduced the information mirroring model, which was his ideal product lifecycle management tool with only one goal. 
    The goal was to gather enhanced information about the real system to minimize the waste of the system's sources such as energy, 
    time and material. Initially, this model had four main parts. The real system, 
    virtual system, connection between the real and virtual system and virtual simulations\cite{GrievesPLMBook}. 
    Later, Grieves removed the latter, to simplify the model\cite{Originsofdigitaltwinconcept}. Lastly, after co-authoring with Vicker in 2010, 
    Grieves decided to use the NASA-invented "Digital Twin" word, instead of the information mirroring model\cite{Originsofdigitaltwinconcept}.

    These days, there is evidence that digital twins play a crucial role in the manufacturing industries, 
    life sciences, healthcare, infrastructure and smart cities\cite{Review2}.
    For example, a digital wind farm from General Electric is a good illustration of how building a digital twin helped to design a better turbine, 
    and later is used to collect and analyze the data from the real system for making the process of the real system more efficient \cite{GeneralElectricWindTurbine}. 
    Another fascinating example of the use of digital twins is Philips' virtual heart model. Twin of the heart evolves with the  data generated by ultrasonic sensors to calculate 
    how well the real heart is pumping the blood. This information can be used to predict a potential heart failure, allowing for early intervention and potentially life-saving treatment \cite{PhilipsHearth}. 
    Lastly, FELICE is another interesting example of a digital twin application in manufacturing. In the project, twin models of machines/equipment and 
    agents are utilized to support real-time decision-making and to conduct what-if analysis and experiments. To ensure the quality of these digital twins, a specific Verification \& Validation process is implemented ~\cite{FELICE}.

@@

    \section{State of the art on quality}
    The Oxford English Dictionary defines the word "quality" as a noun or an adjective form. The adjective form indicates, 
    a high standard of excellence as in  "quality products" \cite{OxfordDictionary}. Even though the noun form is defined in multiple ways, the most impactful 
    definition refers to a  standard of an entity that is measured relative to other entities, whether different or similar \cite{OxfordDictionary}.  
    Additionally, quality is the degree to which a set of inherent properties of an entity fulfills the given requirements~\cite{ISO9000}.
    Both of these definitions clearly show the relative aspect of quality, and the following subcategories are the specialization of these definitions.
    \subsection{Product quality}
    A product is a tangible or intangible system that satisfies the needs or wants of a customer. 
    A product can be a physical system like a car, or an abstract system, like a digital twin. Furthermore, product quality is comprised of two aspects~\cite{GrievesPLMBook}.  
    Firstly, quality is an attribute of a product, which refers to the degree to which a product meets its specifications. These product specifications are mostly defined by the supra-systems' subsystems, such as the stakeholders.
    For this aspect, if the stakeholders' expectations or needs are met,  high quality is considered. The second aspect of product quality is the ability to execute to a specific usage standard.
    Unlike the first aspect, standardization is not controllable. Therefore, the product's quality is determined by how well the implied or obligatory standards are met~\cite{GrievesPLMBook}.

    \subsection{Software quality}
    Software is a combination of programs and data that can be utilized by both virtual and physical systems, 
    such as computer systems\cite{OxfordDictionary}. Its quality is determined by how well it fulfills the requirements that were set. However, 
    those requirements may not always reflect the needs of the stakeholders, hence the quality depends on how accurately these requirements were set \cite{IEE730-2014}. 
    As an example, ISO/IEC:25010 has standardized eight attributes, 
    including functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability, and portability, to measure software quality.

    \subsection{Simulation Quality}
    The human brain simulates real systems abstractly either to predict the future state of the system or to gather information about the past state of the system 
    \cite{MobusSystemTheory}. However, these days, many simulation processes are done by virtual systems. For example,  software programs such as ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} enable users 
    to build a simulation model to make predictions and get information about the past - as well as the current state - of the system.  
    Quality characteristics of these simulation models must be evaluated by the validation and verification techniques \cite{StewartSimulation} \cite{VerificationValidationSergent} \cite{OsmanBalci}.

    Validation is the process of evaluating the simulation quality in comparison to the real system from the perspective of its intended applications. 
    On the other hand, verification is a procedure to evaluate the implementation of the simulation model and 
    its associated data concerning the conceptual description and specifications of the model developer\cite{StewartSimulation}\cite{VerificationValidationSergent}. 
    These techniques are broadly categorized into six areas: informal, static, dynamic, 
    symbolic, constraint, and formal techniques \cite{balcicategories}\cite{balcitechniques}. Formal techniques involve mathematical formality, whereas informal techniques rely on 
    human intervention and reasoning. Although mathematical techniques are more precise, informal techniques are more commonly used \cite{balcicategories}.

    \subsection{Digital twin quality}
    To analyze the state of the digital twin quality, a literature analysis was executed. 
    The analysis especially focused on how the digital twin quality is mentioned and assessed within the academic dissertations. Therefore, various tools, such as Scopus and Google Scholar were 
    used to perform an extensive literature analysis on digital twin publications. However, due to the vast amount of available literature, the scope of the research was narrowed down, resulting in the identification of 
    150 dissertations linked to digital twin quality, verification and validation. After a thorough review of these, only 17 were considered relevant for this paper, and as a result following findings were revealed.

    First, He Zhang et al. developed a consistency evaluation approach for digital twin models, which can be used to assess their quality. 
    The authors also discuss essential concepts, such as consistency between real and virtual systems and ultra-fidelity models~\cite{ZHANGEVALUATIONMETHOD}.

@@

    Selch et al. presented a machine-learning approach based on Bayesian networks to track the quality of the digital twin. 
    The unique aspect of this study is that the authors determined the contributions of subsystems to forecast the overall quality of the digital twin, 
    rather than just analyzing it as a single system. The digital couplings, which are linkages between the subsystems, are also identified as a source of extra uncertainty. 
    However, since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated~\cite{QualityMonitoringofCoupledDigitalTwins}.

@@

    Finally, Shotaro Hamato et al. demonstrated successful real-time anomaly detection using the Unscented Kalman Filter with the digital twin model. 
    However, determining the appropriate threshold for anomaly detection remains problematic~\cite{JapeneseKalmanFilterCorrectness}.

    These dissertations provide valuable insights into various aspects of digital twin quality assessment, including model consistency, stability, and validation, as well as machine learning-based approaches and real-time anomaly detection. 
    However, the identified open problems, including modeling realism, data uncertainty, system dynamics, use-case alignment, and reporting invalid modes, call for further research in the field to improve the quality and reliability of digital twins. Moreover, 
    the lack of well-defined quality parameters for digital twins puts forward a significant challenge in ensuring their quality, which necessitates the development of appropriate quality metrics and standards for digital twins.

@@

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%RESULTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Results}

    \begin{table}[h!]
    \begin{center}
    \label{tab:Table1}
    \caption{Mapping of digital twin attributes to the results of the manual reviews: In cases where an attribute is mapped, the "artifact.qualityattribute.value" is incremented by 1. }
    \renewcommand{\arraystretch}{1.25}
    \scalebox{0.70}{
    \begin{tabular}{l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l@{\hspace{1cm}}l}
        \textbf{Findings} & \textbf{Correctness} & \textbf{Completeness} & \textbf{Fidelity} & \textbf{Efficiency} & \textbf{Evolvability}\\
        \hline
        \textbf{Finding 1} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 2} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 3} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 4} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 5} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 6} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 7} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 8} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 9} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 10} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 11} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 12} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 13} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 14}&~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 15} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 16} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 17} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 18} &~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ \\
        \textbf{Finding 19} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 20} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
        \textbf{Finding 21} &~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~0~~~~~~~~~ & ~~~~~~~~~1~~~~~~~~~ \\
    \end{tabular}
    }
    \end{center}
    \end{table}
